Planar Maximal Covering with Ellipses

### 2019-05-07 quali/quali.presentation/slides.tex
WIP

	\begin{itemize}
		\item Introduce at first for networks. Facilities are placed on nodes, covering a radius of neighboring vertexes.
	\end{itemize}
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
		\item One disk is 3SUM-Hard \autocite{3SUM-kopelowitz:2014}.
		\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms.
		\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm.
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case.
		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm.
	\end{itemize}
\end{itemize}

@@

\section{Preliminaries}

@@

	\begin{itemize}
		\item $MCD$ is as difficult the problem of given $n$ numbers, find three of them that sum to $0$. Proved by \autocite{aronov:2008}.

@@

	\begin{equation*}
	\max_q \sum_{D_k \cap q \neq \emptyset} w_k,
	\end{equation*}

	\begin{itemize}
		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$.
		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.
		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
	\end{itemize}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}
	\begin{figure}
		\only<1>{\caption{An instance of $MCD(\Pp, 1)$.}}
		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
		\only<3>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
		\only<1>{\includegraphics[scale=0.55]{figures/mwc_1.pdf}}
		\only<2>{\includegraphics[scale=0.55]{figures/mwc_2.pdf}}
		\only<3>{\includegraphics[scale=0.55]{figures/mwc_3.pdf}}
		%\only<2>{\input{figures/intro_b.tex}}
		\source{Elaborated by the author.}
	\end{figure}
\end{frame}

@@

	Let $D_i$ (at the origin) and $D_j$ be two unit disks that intersect at two points.

@@

\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by

	\begin{equation*}
	\max_q |\Pp \cap E(q)|,
	\end{equation*}

	\begin{itemize}
		\item $E(q)$ is an axis-parallel ellipse with center point $q$.
		\item Assuming unit weights for now.
		\item Same algorithm for one disk.
	\end{itemize}

@@

	\begin{equation*}
	\max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|},
	\end{equation*}

	\begin{itemize}
		\item $\E$ is a set of $m$ ellipses.
		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
		\item \autocite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
	\begin{algorithm}[H]
		%\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
		\begin{algorithmic}[1]
			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			\STATE $Z \gets \{\}$
			\STATE $Cov \gets \{p_i\}$
			\FOR{$cnt=1..2$} 
			\FOR{$a \in A$}
			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
			\IF{$a$ is a starting angle}
			\STATE $Cov \gets Cov \cup \{p_a\}$
			\ELSE
			\STATE $Cov \gets Cov \setminus \{p_a\}$
			\ENDIF
			\STATE $Z \gets Z \cup \{Cov\}$
			\ENDFOR
			\ENDFOR

@@

>>>>

	\begin{itemize}
		\item Introduce at first for networks \autocite{church:1974}. Facilities are placed on nodes, covering a radius of neighboring vertexes.
	\end{itemize}
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
		\item Introduced by \autocite{church:1984}.
		\item One disk is 3SUM-Hard \autocite{3SUM-kopelowitz:2014}.
		\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms.
		\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm.
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case.
		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm.
	\end{itemize}
\end{itemize}

@@

%\section{Preliminaries}

@@

	\begin{itemize}
		\item $MCD$ is as difficult the problem of given $n$ numbers, find three of them that sum to $0$ (3SUM-HARD). Proved by \autocite{aronov:2008}.

@@

	\begin{equation*}
	\max_{q\in\R^2} \sum_{D_k \cap q \neq \emptyset} w_k,
	\end{equation*}

	\begin{itemize}
		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.

		\item The weight of a clique is the sum of the weights of the disks that intersect with it.

		\item In our case, we just want a point from the optimum clique.

		\item Given an instance $MCD(\Pp, 1)$: fix the disk centers at $\Pp =\{p_1,\dots,p_n\}$ with weights $w_k=w(p_k)$.

		%\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
	\end{itemize}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
	\begin{figure}
		\only<1>{\caption{An instance of $MCD(\Pp, 1)$. We will show how an instance of the Maximum Weight Clique Problem is constructed from it.}}
		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}
		\only<3>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}
		\only<1>{\includegraphics[scale=0.50]{figures/mwc_1.pdf}}
		\only<2>{\includegraphics[scale=0.50]{figures/mwc_2.pdf}}
		\only<3>{\includegraphics[scale=0.50]{figures/mwc_3.pdf}}
		%\only<2>{\input{figures/intro_b.tex}}
		\source{Elaborated by the author.}
	\end{figure}
\end{frame}

@@

	Let $D_i$ (at the origin) and $D_j$ be two unit disks that have their corresponding circles intersect at two points.

@@

\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, and $\Pp=\{p_1,\dots,p_n\}$ is a set of $n$ points with each point having a positive weight $w_i$, an optimal solution of $MCE(\Pp, a, b)$ is given by

	\begin{equation*}
	\max_q w(\Pp \cap E(q)),
	\end{equation*}

	\begin{itemize}
		\item $E(q)$ is an axis-parallel ellipse with center point $q$.
		\item $w(A)$, $A \subset \Pp$, is the sum of the weights of every point in $\Pp$.
		\item Same algorithm for one disk.
	\end{itemize}

@@

	\begin{equation*}
	\max_{q_1, \dots, q_m}{w(\bigcup_{i=1}^{m} \Pp \cap E_i(q_i))},
	\end{equation*}

	\begin{itemize}
		\item $\Pp$ is a set of $n$ points, $\E$ is a set of $m$ ellipses.
		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
		\item \autocite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
	\begin{algorithm}[H]
		\caption{Adaptation of the algorithm for one disk to produce a candidate list for every ellipse.}\label{algoritmo:mce1}
		\begin{algorithmic}[1]
			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			\STATE $Z \gets \{\}$
			\STATE $Cov \gets \{p_i\}$
			\FOR{$cnt=1..2$} 
			\FOR{$a \in A$}
			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
			\IF{$a$ is a starting angle}
			\STATE $Cov \gets Cov \cup \{p_a\}$
			\ELSE
			\STATE $Cov \gets Cov \setminus \{p_a\}$
			\ENDIF
			\STATE $Z \gets Z \cup \{Cov\}$
			\ENDFOR
			\ENDFOR

@@

\begin{frame}{Maximal Covering by Ellipses}{$m$ Ellipses}
	The modified one-disk-cover algorithm produces a list of candidates of location for each ellipse. An optimal solution is guaranteed to be in this list.
\end{frame}
